Object Naming in Language and Vision: A Survey and a New Dataset

### 2019-11-29 papers/LREC2020/survey.tex
small changes

Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco}, 
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
 % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories? How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ... and it nicely shows that natural names are much more variable than strict categories}
% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.

We expect this dataset to be good to examine the effect of distractors on naming choices in a referential setting, because images contain distractors. \cs{what does this mean, maybe give example?, e.g., from above with dog and dalmatian or so; otherwise the issue with the following part may not be understood}
Moreover, multiple annotations ($2.84$\ on average) allow for some minimal analysis of naming variation.
However, note that not all objects of an image are annotated with REs and corresponding categories, so it may be difficult to analyze the effect of distractors with automatic processing.
While in \refcoco, the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
To sum up, we would recommend \refcoco to study the effect of distractors on object naming in a restricted set of categories.

@@

\gbt{@Sina, pls check that I got this right:}
One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
Another is the fact that it potentially provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
This should make it easier to identify factors intervening in naming choices.
However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze contextual factors for naming.\cs{The explanation of intervening factors in object naming in the background may be a bit more detailed, such as to really understand the drawbacks of the existing datasets with respect to distractors.}

>>>>

Both datasets  \cite{Yu2016} use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco}, 
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
 % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories? How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ... and it nicely shows that natural names are much more variable than strict categories}
% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.

We expect this dataset to be good to examine the effect of context on naming choices in a referential setting, because the images contain complex scenes with other objects of more or less similar categories, i.e.\ so-called distractors \cite{krahmer:2012}.
Moreover, multiple annotations ($2.84$\ on average) allow for some minimal analysis of naming variation.
However, note that not all objects of an image are annotated with REs and corresponding categories, so it may be difficult to analyze the effect of distractors with automatic processing.
While in \refcoco, the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
To sum up, we would recommend \refcoco to study the effect of distractors on object naming in a restricted set of categories.

@@

One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
Another is the fact that it potentially provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
This should make it easier to identify factors intervening in naming choices.
However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze contextual factors for naming.\cs{The explanation of intervening factors in object naming in the background may be a bit more detailed, such as to really understand the drawbacks of the existing datasets with respect to distractors.}
